Dynamic Adaptive Saturated Sliding Mode Control For Deployment of Tethered Satellite System

### 2016-10-04 manuscript.tex
20161004

H(q)\dot S_r+C(q,\dot q)S_r+G(q)=\tau - Y_r\Theta\label{eq:dynamic model 2}

@@

For deriving the control scheme, some properties should be given out in advance.

@@

\Vert \dot q_r\Vert & \le \Xi_4+\alpha\Vert\Delta q\Vert+\beta\Vert\sigma\Vert\\

@@

where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively. Furthermore, one can have $Y_r\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta q,\Delta \dot q,\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi$, in which $\varphi$ is a positive scalar determined according to the system state~\cite{parra2003dynamic}.

@@

in which, the characteristics of the signum above can be obtained by check if the sign of $y=(x_1+x_2)(Sine(x_1)+Sine(x_2))$ is alwasys nonnegative.

@@

As we know, compared with the tension limited in deployment mission, the generalized in-plane and out-of-plane forces are saturated but not regular, hence for avoiding confusion, we specify the following expression

@@

g(\tau) &= \begin{pmatrix}g(\hat\tau_t)\\g(\hat\tau_\theta)\end{pmatrix}\\
R(\tau) &= \begin{bmatrix}R(\hat\tau_t)&0\\0&R(\hat\tau_\theta)\end{bmatrix}.

@@

Sine(\Delta q)=\begin{pmatrix}Sine(\Delta \lambda)\\Sine(\Delta\theta)\end{pmatrix}.

@@

\tau = -g(\delta\varphi F(t) K_dsign(S_{r1})),\label{eq:slider control}

@@

S_{q1} &= Sine(\Delta \dot q+\alpha\Delta q),

@@

\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1K_de^{-2K_1^{-1}F^{-1}(t)}sign(S_{r2})

@@

@@

It is obvious that $S_{q_1}$ is bounded, or exactly saturated, hence $S_{r_1}$ is also bounded if the dynamics can be controlled as desired. In addition, one can select a suitable positive scalar $\gamma$ such that $\gamma\int^t_{t_0}S_{q1}(\varsigma)^\varpi d\varsigma\in[-1,1]$.\par

@@

&S_{r2}^T sign(S_{r2}) \ge  S_{r1}^T sign(S_{r1})\\
&sign(S_{r2})=sign(S_{r1}),

@@

@@

sign(x) = \begin{pmatrix}sign(x_1),sign(x_2),\cdots,sign(x_n)\end{pmatrix}^T,
for a vector $x$. Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinates change $S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $S_{r2}$ holds results in the following expression:
H(q)\dot S_{r2} = -g(\delta\varphi F(t) K_dsign(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.

@@

&= -S_{r2}^Tg(\delta\varphi F(t) K_dsign(S_{r1}))-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
&= -S_{r2}^Tg(\delta\varphi F(t) K_dsign(S_{r1}))-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
&= -S_{r2}^Tg(\delta\varphi F(t) K_dsign(S_{r1}))-S_{r2}^TY_{r2}\Theta+v\dot v\\
&= -S_{r2}^TR(\delta\varphi F(t) K_dsign(S_{r1}))\delta\varphi F(t) K_dsign(S_{r1})-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}

@@

v\dot v =\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})sign(S_{r2}),

@@

utilizing $sign(S_{r1})=sign(S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:

@@

\dot V&\le -S_{r2}^T\delta\varphi  K_1K_dF(t)sign(S_{r2})+S_{r2}^T\varphi sign(S_{r2})+\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})sign(S_{r2})\\
&\le \varphi S_{r2}^Tsign(S_{r2})-\varphi\delta S_{r2}^T K_dsign(S_{r2})

@@

\dot Z = \vert Z\vert^{\hat\alpha} sign(Z),

@@

\tau = -g(\delta\varphi F(t) K_{d1}sign(S_{r3}))

@@

S_{r3} &= S_{q3}+\gamma\int^t_{t_0}\Vert S_{q3}(\varsigma)\Vert^{\hat\alpha}  sign(S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
S_{q3} &= \Delta \dot q+\alpha Sine(\xi\Delta q),\label{eq:Sq3}

@@

\tau = -g(\delta\varphi F(t) K_{d1}sign(S_{r4})),

@@

S_{q4} &= Sine(\Delta \dot q+\alpha\xi\Vert\Delta q\Vert^{\hat\alpha}sign(\Delta q)),\label{eq:Sr4}

>>>>

H(q)\dot S_r+C(q,\dot q)S_r=\tau - Y_r\Theta\label{eq:dynamic model 2}

@@

We define the tracking error as $\Delta q=q-q_d$, in which $q_d$ is the reference trajectory with $q_d(t)\in C^2$. For deriving the control scheme, some properties should be given out in advance.

@@

\Vert \dot q_r\Vert & \le \Xi_4+\alpha\Vert\Delta q\Vert+\gamma\Vert\sigma\Vert\\

@@

where $\zeta_{min}(\cdot)$ and $\zeta_{max}(\cdot)$ mean the minimum and maximum eigenvalues of matrix, respectively, and $\alpha$ and $\gamma$ are controller parameters which will be discussed later on. Furthermore, one can have $Y_r\Theta\le \eta(t)$, in which $\eta(t)=f(\Delta q,\Delta \dot q,\sigma,\Xi_i,t)$ is a state-dependent function, thus $Y_r\Theta$ is usually thought to be a bounded function such that $\vert\eta\vert\le\varphi$, in which $\varphi$ is a positive scalar determined according to the system state~\cite{parra2003dynamic}.

@@

in which, the characteristics of the signum above can be obtained by \textcolor{red}{checking} if the sign of $y=(x_1+x_2)(Sine(x_1)+Sine(x_2))$ is alwasys nonnegative.

@@

As we know, \textcolor{red}{the tension, in-plane and out-of-plane thruster force are all limited during deployment mission, and we describe inputs by using the matrix and vector to predigest the following illation.}

@@

\overrightarrow{g}(\tau) &= \left(g(\hat\tau_t),g(\hat\tau_\theta),g(\hat\tau_\phi)\right)^T\\
R_M(\tau) &= \begin{bmatrix}R(\hat\tau_t)&0&0\\0&R(\hat\tau_\theta)&0\\0&0&R(\hat\tau_\phi)\end{bmatrix}.

@@

\overrightarrow{Sine}(q)=\begin{pmatrix}Sine(\lambda),Sine(\theta),Sine(\phi)\end{pmatrix}^T.

@@

\tau = -\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1})),\label{eq:slider control}

@@

S_{q1} &= \overrightarrow{Sine}(\Delta \dot q+\alpha\Delta q),

@@

\frac{d}{dt}F(t) = \delta\varphi S_{r2}^T K_1K_de^{-2K_1^{-1}F^{-1}(t)}\overrightarrow{sign}(S_{r2})

@@

\overrightarrow{sign}(x) = \begin{pmatrix}sign(x_1),sign(x_2),\cdots,sign(x_n)\end{pmatrix}^T,
for a vector $x=\left(x_1,x_2,,\cdots,x_n\right)^T$.

@@

It is obvious that $S_{q_1}$ is bounded, or exactly saturated, hence $S_{r_1}$ is also bounded if the dynamics can be controlled as desired. In addition, one can select a suitable positive scalar $\gamma$ such that $\gamma\int^t_{t_0}S_{q1}(\varsigma) d\varsigma\in[-1,1]$.\par

@@

&S_{r2}^T \overrightarrow{sign}(S_{r2}) \ge  S_{r1}^T \overrightarrow{sign}(S_{r1})\\
&\overrightarrow{sign}(S_{r2})=\overrightarrow{sign}(S_{r1}),

@@

Introducing the limited input~(\ref{eq:slider control}) and replacing the dynamic coordinates change $S_r$ in Eq.~(\ref{eq:dynamic model 2}) with $S_{r2}$ holds results in the following expression:

@@

H(q)\dot S_{r2} = -\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-C(q,\dot q)S_{r2}-Y_{r2}\Theta.

@@

&= -S_{r2}^T\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-S_{r2}^TC(q,\dot q)S_{r2}+\frac{1}{2}S_{r2}^T\dot H(q)S_{r2}-S_{r2}^TY_{r2}\Theta+v\dot v\\
&= -S_{r2}^T\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-S_{r2}^TY_{r2}\Theta+\frac{1}{2}S_{r2}^T(\dot H(q)-2C(q,\dot q))S_{r2}+v\dot v\\
&= -S_{r2}^T\overrightarrow{g}(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))-S_{r2}^TY_{r2}\Theta+v\dot v\\
&= -S_{r2}^TR_M(\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1}))\delta\varphi F(t) K_d\overrightarrow{sign}(S_{r1})-S_{r2}^TY_{r2}\Theta+v\dot v.\label{eq:V1_1}

@@

v\dot v =\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\overrightarrow{sign}(S_{r2}),

@@

utilizing $\overrightarrow{sign}(S_{r1})=\overrightarrow{sign}(S_{r2})$ and $K_1$ proceeds to rewrite Eq.~(\ref{eq:V1_1}) as:

@@

\dot V&\le -S_{r2}^T\delta\varphi  K_1K_dF(t)\overrightarrow{sign}(S_{r2})+S_{r2}^T\varphi \overrightarrow{sign}(S_{r2})+\varphi\delta S_{r2}^T K_1K_d(F(t)-K_1^{-1})\overrightarrow{sign}(S_{r2})\\
&\le \varphi S_{r2}^T\overrightarrow{sign}(S_{r2})-\varphi\delta S_{r2}^T K_d\overrightarrow{sign}(S_{r2})

@@

\dot Z = \vert Z\vert^{\hat\alpha} \overrightarrow{sign}(Z),

@@

\tau = -\overrightarrow{g}(\delta\varphi F(t) K_{d1}\overrightarrow{sign}(S_{r3}))

@@

S_{r3} &= S_{q3}+\gamma\int^t_{t_0}\Vert S_{q3}(\varsigma)\Vert^{\hat\alpha}  \overrightarrow{sign}(S_{q3}(\varsigma))d\varsigma\label{eq:Sr3}\\
S_{q3} &= \Delta \dot q+\alpha \overrightarrow{Sine}(\xi\Delta q),\label{eq:Sq3}

@@

\tau = -\overrightarrow{g}(\delta\varphi F(t) K_{d1}\overrightarrow{sign}(S_{r4})),

@@

S_{q4} &= \overrightarrow{Sine}(\Delta \dot q+\alpha\xi\Vert\Delta q\Vert^{\hat\alpha}\overrightarrow{sign}(\Delta q)),\label{eq:Sr4}
